Quality Definitions of Qualities

### 2019-10-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex

\subsection{Robustness}

@@

>>>>

\subsection{Robustness}
The degree to which a system or component can function correctly in the presence of invalid inputs or stressful environmental conditions \cite{IEEEStdGlossarySET1990}.
The quality can be further informally refined as the ability of a software to keep an acceptable behavior, expressed in terms of robustness requirements, in spite of exceptional or unforeseen execution conditions (such as the unavailability of system resources, communication failures, invalid or stressful inputs, etc.) \cite{fernandez2005model}.

@@

The ease with which a system or component can be transferred from one hardware or software environment to another \cite{IEEEStdGlossarySET1990}. An application is portable across a class of environments to the degree that the effort required to transport and adapt it to a new environment in the class is less than the effort of redevelopment \cite{mooney1990strategies}.
